---
title: "DSCI301 HW 5"
author: "Randy Nuhfer"
date: "9/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library loading...

```{r}
library(here)
library(tidyverse)
```

## Problem 1:

```{r}
Spotify_path <- here("datasets_1833_3172_data.csv")
Spotify <- read_csv(Spotify_path,
                    col_types = cols(
  X1 = col_double(),
  acousticness = col_double(),
  danceability = col_double(),
  duration_ms = col_double(),
  energy = col_double(),
  instrumentalness = col_double(),
  key = col_factor(),
  liveness = col_double(),
  loudness = col_double(),
  mode = col_factor(),
  speechiness = col_double(),
  tempo = col_double(),
  time_signature = col_double(),
  valence = col_double(),
  target = col_factor(),
  song_title = col_character(),
  artist = col_character()
))
```
After reading in the data I changed three columns. Firstly, I changed the key column to a factor column because there is only a set number of keys. Secondly, I also changed mode to a factor as it only indicates whether the song is in a major key or minor key. Finally I chnaged the target column to a factor as well as this only indicates whether or not the creator of this data set liked that particular song.


## Problem 2:

```{r}
Spotify %>%
    ggplot(aes(x = loudness)) +
    geom_histogram(bins = 15, fill = "blue", color = "red") +
    labs(title = "Distribution of loudness (in decibels)")
```

Looking at this graph we can clearly see most songs have a loundness around -5 decibels.

## Problem 3:

```{r}
Spotify %>%
    ggplot(aes(x = loudness, y = liveness)) +
    geom_point(color = "blue") +
    labs(title = "Loudness vs Liveness")
```

Looking at this graph we can see that a large portion of songs that are rather loud tend to be performed without a live audience present. This may indicate that in the presents of an audience the audience itself drowns out the music a bit, while the louder songs are more than likely recorded in a studio with high end recording equipment to get that louder, crystal clear sounds.



